---
title: "Initial Korean covid 19"
author: "Valerie Rodriguez"
date: "03/30/2023"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(digits=2)
require(tidyverse)
require(tigerstats)
require(lubridate)
kRdata <- read.csv(file = 'kRdata.csv')
kRdata <- kRdata %>%
mutate(across(where(is.character), as.factor))

```
### Data is from the Patient_Info dataset from South Korea 1 Jan to 1 May 2020
### This data was retrieved from a downloadable zip file from kaggle

Some of the data was uncoded for sex - sex must be just male or female
77 of the data entries were coded sex  as blank, so we omit these.
state of a patient must be died or alive - we adjust that as well   
  
# Your Question - Is dying independent of sex?






## Graphical results - use ggplot commands to do this  

```{r}
barchartGC(~result + Sex,data=kRdata)
barchartGC(~result + Sex,data=kRdata, type="percent")

```


From this data we can see that males died more than females. The frequency of those who are alive is much higher than the frequency of those who are dead. In general there are more females than males.

  
## Numerical results

```{r}
table1 <- xtabs(~result + Sex, data=kRdata)
rowPerc(table1)
colPerc(table1)
```


For every 1.4 deaths of women there was 3 male deaths. There was 56% females who lived and 36% who died which is a 14:9 percent ratio. There was 44% males that lived and 64% who died which is a 11:16 percent ratio. In comparison males died and at much higher rate than females.



## Inferential results 

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```

In this data set we are provided with actual numbers of those who lived and died. In the plot above we were proved categorical percentages. It was expected in this data that 39 females were going to die and 30 males were going to die. The observed counts showed that only 25 females died and 44 males died. This disease has killed significantly more males than expected. The odds ratio is 2.3 which means that a male is 2.3x more likely to die from Covid than a female.


## Conclusions

In conclusion Covid-19 in Korea killed significantly more men than women. A male is 2.3x more likely to die from Covid than a female is. Depending on your sex and if your a male you are at a much higher risk of dying. It was expected that  significantly more females would die than males but when the actual results were taken it was the exact opposite. Even though the results from graphical data showed that there are more females in the population compared to men the ratio remains basically the same and more males died regardless.

